---
title: "Who does more pushups"
author: "Damaris Avila"
date: "October 7 2015"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.
The "tigerstats" data frame includes 30 observations on three variables. The three variables are weight, pushups, and position. The weight variable is the weight of each subect in pounds. The pushups variable is the number of pushups completed by each subject. The position variable is the type of position played by the subject. It is either "line" or "skill". Line positions require high body mass and skill positions require a lot of running. 

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of running and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
What methods are appropriate for analyzing our data? The choice depends on the type of variables we are researching with our Research Question.  

**Weight and Pushups** are numerical variables  
**Position** is a factor variable.  

 Weight and pushups are numerical variables.
  This makes sense and is proven by looking in the help tab. Also, by looking at the data frame "pushups" you can see that the values of the variables "weight", and "pushups" are numbers.  
  
  Position is a factor variable where there are only two options for the value of this variable. Either the value is LINE or it is SKILL. This value is the type of position played by the subject. This can be confirmed through the help tab or through the data frame "pushups".    
  
  A good way in analyzing these variables to determine whether a line player or a skill player does more pushups would be using a bar chart graph. I will make a bar chart with "position" as the x-axis and "pushups" as its y-axis.   
  
  A good numerical way to analyze these variables is using the mean as well as the median for each position and comparing the results of the two.  
  
  Both methods, graphical and numerical, have been chosen. The following are the results acquired using these methods.    
  
# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
I have both graphical and numerical methods, so I have both graphical and numerical results. 

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->

The following is the graph comparing the number of pushups done, seperated by position. Position is the x-axis, and number of pushups is the y-axis. 

```{r}
bwplot(pushups ~ position,
	data = pushups,
	main = list(label="Number of Pushups by Position",
		cex = 1.5),
	xlab = "Position",
	ylab = "Number of Pushups Completed")
```

The alignment of each of the boxes make it easy to see that the number of pushups completed by the LINE players is significantly lower than the number of pushups completed by the SKILL players. 

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position, data=pushups)
```
There were 22 SKILL players and 8 LINE players in this study. SKILL players appear to be able to complete more pushups on average in a two minute time frame:the median for SKILL players is 47.5 pushups, compared to the LINE players with a median of 14.5. As well as the mean: the mean for SKILL players is 49.72727, while the mean for LINE players is 17.12500.

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
*My null hypothesis is:*  
**H~0~** : There is NO difference between the number of pushups completed by SKILL players and the number of pushups completed by LINE players.   

*My alternate hypothesis is:*  
**H~a~** : There IS a difference between the number of pushups completed by SKILL players and the number of pushups completed by LINE players.  


The output of the ttest is as follows:
```{r}
t.test(pushups~position, data=pushups)
```
According to the extremely small p-value, the chances the null hypothesis would result to be TRUE
are almost nonexistant. This low p-value suggests that our sample provides enough evidence that we can **reject our null hypothesis**.


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->
*Both my numerical and graphical results indicate that SKILL players are able to do more pushups in a two minute interval, on average than LINE players.* It is still only one sample from Georgetown College. It may differ from school to school, as their training and fitness level may differ. It is still a question as to whether this data is strong enough to conlude that the results from this sample is the a true representation of the population of all LINE and SKILL players at large. 
